{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-23 paper/paper.tex
removed misplaced word
interleaved between what…

The latter two are the interesting ones. If a thread is \textit{always high} it
can not leaks any information into low, because it never only gets in touch
with low program points. So these threads can safely be interleaved by the
scheduler.

>>>>

The latter two are the interesting ones. If a thread is \textit{always high} it
can not leaks any information into low, because it never gets in touch
with low program points. So these threads can safely be interleaved between any
other threads by the scheduler.
